---
title: "Liam Kettle's CV"
author: Liam Kettle
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "data/",  
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}


```

# Aside

------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```

## UX Methods {#methods}

```{r}
CV %>% print_aside_section('research')
```

## Statistical Analyses {#stats}

```{r}
CV %>% print_aside_section('stats')
```

## Coding / Tools {#code}

```{r}
CV %>% print_aside_section('code')
```

## Disclaimer {#disclaimer}

Made with the R packages [**pagedown**](https://github.com/rstudio/pagedown) and [***datadrivencv***](https://github.com/nstrayer/datadrivencv).

The source code is available on [github.com/LiamKettle/resume](https://github.com/LiamKettle/resume).

Last updated on `r Sys.Date()`.

# Main

## **Liam Kettle, M.S.** {#title}

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 

```

## Education {data-icon="graduation-cap" data-concise="true"}

```{r}
CV %<>% print_section('education')
```

## Research Experience {data-icon="laptop"}

```{r}
CV %<>% print_section('research_positions')
```

<!-- ## Teaching Experience {data-icon="chalkboard-teacher"} -->

<!-- ```{r} -->
<!-- CV %<>% print_section('teaching_positions') -->
<!-- ``` -->

## Select Publications {data-icon="book"}

```{r}
CV %<>% print_academia_section('academic_articles')
```

## Select Awards {data-icon="award"}

```{r}
CV %<>% print_minor_section('award')
```

## Professional Service & Leadership {data-icon="user-tie"}

```{r}
CV %<>% print_section('service')
```